\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{VeritasAd: Multimodal Advertising Detection Platform}
\author{VeritasAd Team}
\date{2026}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Introduction}
VeritasAd is a multimodal system for detecting hidden advertising in video content.
The platform combines visual, audio, and textual signals to produce evidence-based
reports for compliance and brand safety.

\section{Related Work}
This section reviews prior work on multimodal advertising detection, disclosure
classification, and brand/logo recognition. Include key academic references
and industry systems.

\section{System Architecture}
Describe the overall architecture: frontend, backend API, task processing,
ML pipeline, and storage. Provide component diagrams and data flow charts.

\subsection{Backend}
FastAPI with async SQLAlchemy, Redis, and Celery background tasks.

\subsection{ML Pipeline}
CLIP for visual detection, Whisper for audio transcription, and LLM-based
disclosure detection.

\section{Experiments and Evaluation}
Document dataset composition, labeling methodology, and evaluation metrics.
Report F1, precision, and recall for disclosure detection, and mAP for logo detection.

\section{Results}
Summarize performance across modalities and discuss system latency,
resource usage, and accuracy.

\section{Conclusion}
Summarize contributions and outline future improvements.

\appendix
\section{Code Samples}
Include key snippets or pointers to source code files.

\section{Reports}
Include sample PDF reports generated by the system.

\end{document}